\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-07-11 fluB.tex
Enable cross-references between main and supp text.
Add 1600 genomes LD, move figures to right places.
Fix #34

@@

We show that despite extensive reassortment, three of the eight segments -- two segments coding for components of the influenza B virus polymerase, PB1 and PB1, and the surface glycoprotein HA -- still survive as distinct Victoria and Yamagata lineages, which appear to be co-adapted to the point where virions which do not contain PB1, PB2 or HA segments derived entirely from either the Vic or the Yam lineage have rarely been isolated and only circulate as transient lineages once isolated.
In other segments (PA, NP, NA, MP and NS) a single lineage has introgressed into the opposing background and been fixed in the influenza B population: Yam for PA, NP, NA and MP and Vic for NS.
This has occurred through repeated reassortments and subsequent fixation of reassortant genome constellations within the influenza B population.

\begin{figure}[h]
 \centering		
	\includegraphics[width=0.45\textwidth]{figures/TreeFigure2}
	\caption{\textbf{Schematic analysis of reassortment patterns.}
	A) We begin by assigning sequences falling on either side of a specified bifurcation within each segment tree to different lineages, in this case, the Victoria and Yamagata bifurcation that occurred in the early 1980s.
	B) We then transfer lineage labels from one tree to the same tips in another tree.
	Transitions between labels along this second tree thus indicate reassortment events that combine lineages falling on different sides of the Vic/Yam bifurcation in the first tree.
	C) A reassortment graph depiction shows that tip number 6 is determined to be a reassortant based on B).
	}
	\label{methodFig}
\end{figure}

@@

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.65\textwidth]{supp_figures/InfB_LDcircle.1600.aa.ChiSqdf.minorCutoff1percent.png}
	\caption{\textbf{LD comparison between influenza B proteins.}
Pairwise comparisons of linkage disequilibrium between amino acid sites on influenza B proteins in the secondary dataset.
Many polymorphic amino acid sites on PB1, PB2 and HA proteins exhibit high LD between themselves, followed by the NA protein.
This is evidence of a considerable number of co-assorting alleles within these proteins.}
	\label{segmentLD}
\end{figure}

@@

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.85\textwidth]{supp_figures/InfB_methodSpeciesTree.pdf}
	\caption{\textbf{Calculating $\dtmrca$ from a species tree perspective.}
Consider an organism that has diverged into 3 taxa (A, B, C) with a genome comprised of 3 segments (blue, green and red).
Due to reassortments taxa A and B share a slightly more recent TMRCA in the red segment, likewise for taxa B and C in the green segment.
By comparing differences in TMRCAs between taxa A-B, A-C and B-C in blue, red and green segments we would find that the red segment has a lower `reassortment distance' (X) than the green segment (Y).
}
	\label{speciesTree}
\end{figure}

@@

\bibliographystyle{mbe}
\bibliography{fluB}

>>>>

% reference figures across documents
\usepackage{xr}
\externaldocument{fluB_supp}

@@

We show that despite extensive reassortment, three of the eight segments -- two segments coding for components of the influenza B virus polymerase, PB1 and PB2, and the surface glycoprotein HA -- still survive as distinct Victoria and Yamagata lineages, which appear to be co-adapted to the point where virions which do not contain PB1, PB2 or HA segments derived entirely from either the Vic or the Yam lineage have rarely been isolated and only circulate as transient lineages once isolated.
In other segments (PA, NP, NA, MP and NS) a single lineage has introgressed into the opposing background and been fixed in the influenza B population: Yam for PA, NP, NA and MP and Vic for NS.
This has occurred through repeated reassortments and subsequent fixation of reassortant genome constellations within the influenza B population.

\begin{figure}[h]
 \centering		
	\includegraphics[width=0.45\textwidth]{figures/TreeFigure2.png}
	\caption{\textbf{Schematic analysis of reassortment patterns.}
	A) We begin by assigning sequences falling on either side of a specified bifurcation within each segment tree to different lineages, in this case, the Victoria and Yamagata bifurcation that occurred in the early 1980s.
	B) We then transfer lineage labels from one tree to the same tips in another tree.
	Transitions between labels along this second tree thus indicate reassortment events that combine lineages falling on different sides of the Vic/Yam bifurcation in the first tree.
	C) A reassortment graph depiction shows that tip number 6 is determined to be a reassortant based on B).
	}
	\label{methodFig}
\end{figure}

@@

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.65\textwidth]{figures/InfB_LDcircle.1600.aa.ChiSqdf.minorCutoff1percent.png}
	\caption{\textbf{LD comparison between influenza B proteins.}
Pairwise comparisons of linkage disequilibrium between amino acid sites on influenza B proteins in the secondary dataset.
Many polymorphic amino acid sites on PB1, PB2 and HA proteins exhibit high LD between themselves, followed by the NA protein.
This is evidence of a considerable number of co-assorting alleles within these proteins.}
	\label{segmentLD}
\end{figure}

@@

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.85\textwidth]{figures/InfB_methodSpeciesTree.pdf}
	\caption{\textbf{Calculating $\dtmrca$ from a species tree perspective.}
Consider an organism that has diverged into 3 taxa (A, B, C) with a genome comprised of 3 segments (blue, green and red).
Due to reassortments taxa A and B share a slightly more recent TMRCA in the red segment, likewise for taxa B and C in the green segment.
By comparing differences in TMRCAs between taxa A-B, A-C and B-C in blue, red and green segments we would find that the red segment has a lower `reassortment distance' (X) than the green segment (Y).
}
	\label{speciesTree}
\end{figure}

@@

\bibliographystyle{mbe.bst}
\bibliography{fluB}
